%---------------------------------------------
%			RESUME
%---------------------------------------------
\documentclass[10pt]{article}

%---------------------------------------------
%	BASIC PACKAGE DECLARATIONS
%---------------------------------------------
\usepackage[top=0.3in, bottom=0.3in, left=0.3in, right=0.5in]{geometry}
\usepackage{array, xcolor}
\usepackage{mathpazo}
\usepackage[parfill]{parskip} % Remove paragraph indentation

\begin{document}
%---------------------------------------------
%		     TITLE
%---------------------------------------------
\begin{center}
{\Large \bf Vivitsu Maharaja}
\date{}
\thispagestyle{empty}
\smallskip \\
%---------------------------------------------
%	     CONTACT INFORMATION
%---------------------------------------------
{\small 3800 SW 34\textsuperscript{th} Street, Apartment Z251, Gainesville, FL $\diamond$ (352) 278-5449 $\diamond$ vmaharaja@ufl.edu}
\end{center}

%---------------------------------------------
%	           OBJECTIVE
%---------------------------------------------
\MakeUppercase{\bf Objective}
%\medskip \\
%\hrule

To obtain a position where I can leverage and enhance my skills \& experience while working on challenging problems in computer engineering \& software development.

%---------------------------------------------
%	           EDUCATION
%---------------------------------------------
\MakeUppercase{\bf Education}
%\medskip \\
%\hrule

{\bf University of Florida}, Gainesville, Florida\\
\textit{Master of Science, Electrical \& Computer Engineering}\hfill{\bf May 2014}\\
Relevant Coursework: Computer Architecture, Parallel Computer Architecture, Distributed Computing, Cloud Computing, Computer Communications, Probability \& Random Processes.\\
GPA: 3.16/4.0 %\medskip \\

{\bf Dharmsinh Desai University}, Nadiad, India\\
\textit{Bachelor of Engineering, Electronics \& Communication}\hfill{\bf May 2011}\\
Selected Coursework: Embedded Systems, Data \& Computer Communication, Advanced Microprocessors, Probability \& Statistics, Communication Systems, C Programming.\\
GPA: 62/100

%---------------------------------------------
%		WORK EXPERIENCE
%---------------------------------------------
\MakeUppercase{\bf Work Experience}
%\medskip \\
%\hrule

{\bf Advanced Computing \& Information Systems Lab}, University of Florida\\
\textit{Research Volunteer}, iDigBio Project\hfill{\bf May 2013 - Present} \smallskip \\
%---------------------
%	PROJECT - 1
%---------------------
Working on the implementation, evaluation \& tuning of text-based information retrieval systems using NoSQL datastores. \smallskip \\
Developed a Java application that fetches JSON objects from a URL and adds them to Riak. Bucket creation, key management \& interfacing with Riak are all managed automatically by the application. \smallskip \\
Responsible for the setup and management of Hadoop \& Riak clusters. %\medskip

{\bf Volansys Technologies}, Ahmedabad, India\\
\textit{Embedded Engineer}\hfill{\bf November 2011 - July 2012} \smallskip \\
%---------------------
%	PROJECT - 1
%---------------------
Developed a USB 2.0 (Enhanced Host Controller Interface) Host Controller driver in x86 assembly, which allowed desktops/tablets with Intel x86 processors to PXE (Pre-boot eXecution Environment) boot via a network using an USB to Ethenet adapter. The driver was part of an application which ran in real-mode, without any OS involvement \& under significant memory \& run-time constraints. \smallskip \\
Developed software components to manage the PCI bus, negotiate ownership with the BIOS subsystem and added support for multiple vendor adapters, as part of the overall PXE application. \smallskip \\
%Handled responsibility for all aspects of the project, including development, maintenance, documentation \& client interaction.\smallskip \\
%---------------------
%	PROJECT - 2
%---------------------
Worked with a team of 2 engineers to develop a software feature that would allow multiple broadcast domains in a wireless router to form a VLAN (Virtual LAN). The wireless router was based on the MIPS \& VxWorks platforms.

%---------------------------------------------
%	          PROJECTS
%---------------------------------------------
\MakeUppercase{\bf Projects}
%\medskip \\
%\hrule

%---------------------
%	PROJECT - 1
%---------------------
{\bf Web Server for Location Based Applications} \textit{using Go \& Redis}\hfill{\bf February 2013 - April 2013} \smallskip \\
Designed and implemented a highly concurrent web server that accepts a client's location and presents choices to view different resources based on the entered location. \smallskip \\
Used TLS encryption to secure client connections with the server. \smallskip \\
Added support for user account creation \& user's location history. %\medskip

%---------------------
%	PROJECT - 2
%---------------------
%{\bf Face Recognition using Artificial Neural Networks} \textit{using C \& CUDA}\hfill{\bf February 2013 - April 2013} \smallskip \\
%Designed and implemented an application that performed face recognition using an artificial neural network on a CPU/GPU cluster. \smallskip
%Used Principal Component Analysis for feature extraction and error backpropagation to train the network. %\medskip

%---------------------
%	PROJECT - 3
%---------------------
{\bf Distributed Fault-Tolerant Stock Exchange System} \textit{using Java \& JGroups}\hfill{\bf April 2013} \smallskip \\
Implemented a stock exchange system that used fault-tolerant, virtually synchronous replicas to perform stock trades. \smallskip \\
The system was designed to handle large number of client connections \& trade requests to different nodes in the system. \smallskip \\
Client information, trade requests \& stock data are preserved by the system. %\medskip

%---------------------
%	PROJECT - 4
%---------------------
%{\bf Distributed Control of Currency Exchange Value} \textit{using Java}\hfill{\bf March 2013} \smallskip \\
%Implemented totally-ordered multicasting using Lamport's logical clocks. The goal was to keep the replicas on the 3 machines, which shared a currency %exchange value, consistent using active replication protocol. %\medskip

%---------------------
%	PROJECT - 5
%---------------------
%{\bf DNS Server} \textit{using Java RMI}\hfill{\bf February 2013} \smallskip \\
%Implemented a DNS server that supports recursive as well as iterative name resolution with support for server side caching using Java RMI. %\medskip

%---------------------
%	PROJECT - 6
%---------------------
{\bf Gossip based Topology Management in Peer-to-Peer Systems} \textit{using C, Java}\hfill{\bf January 2013} \smallskip \\
Implemented the T-Man gossip based topology management protocol for peer to peer overlay networks, which achieved various topologies for a cluster of nodes based on different distance functions. This implementation was done in C. \smallskip \\
Modified the T-Man implementation so that it would adapt it's topology at runtime to changes in the radius of the network. This implementation was done in Java. %\medskip

%---------------------
%	PROJECT - 7
%---------------------
%{\bf Simulation of Dijkstra's Algorithm} \textit{using C}\hfill{\bf July 2010 - November 2010} \smallskip \\
%Developed a program that would take a user-defined network graph as input and find the shortest path between any two nodes in the graph using %Dijkstra's algorithm. %\medskip

%-----------------------------
%	PRESENTATION - 1
%-----------------------------
%{\bf ``Fundamentals of Switching \& Mobile Number Portability in a GSM network''}\hfill{\bf April 2011} \smallskip \\
%Prepared and presented a report on the operation of a large scale GSM network, including switching principles and mobile number portability %implementation. %\medskip

%---------------------------------------------
%	           SKILLS
%---------------------------------------------
\MakeUppercase{\bf Skills}
%\medskip \\
%\hrule

{\bf Programming Languages:} x86 Assembly, C, Java, Go, MPI, CUDA \& \LaTeX\ \\
{\bf Technologies:} Hadoop, Riak, Redis, Git, Subversion\\
{\bf Operating Systems}: GNU/Linux, OS X, Windows\\

\end{document}
