%---------------------------------------------
%			RESUME
%---------------------------------------------
\documentclass[10pt, letterpaper]{article}

%---------------------------------------------
%	BASIC PACKAGE DECLARATIONS
%---------------------------------------------
\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
%\usepackage{array, xcolor}
%\usepackage{mathpazo}
%\usepackage[parfill]{parskip} % Removes paragraph indentation, but screws up the alignment of hfill. Use the next line
\usepackage{parskip}
%\usepackage{hyperref}
%\usepackage{fancyhdr}
\usepackage{enumitem}
\setlist{nolistsep} % No space between list items

% Add filled diamond instead of outlined diamond
\DeclareSymbolFont{extraup}{U}{zavm}{m}{n}
\DeclareMathSymbol{\vardiamond}{\mathalpha}{extraup}{87}

%\addtolength{\oddsidemargin}{-.975in}
%\addtolength{\evensidemargin}{-.975in}
%\addtolength{\textwidth}{1.95in}
%\addtolength{\topmargin}{-1.1in}
%\addtolength{\textheight}{2.75in}

%\pagestyle{fancy}

%\pagenumbering{gobble} % Adding this to suppress page numbering while keeping footer

%\lfoot{All source code, including the \LaTeX\ source for this document can be found at \texttt{https://github.com/vivitsu}}
%\renewcommand{\headrulewidth}{0.4pt}
%\renewcommand{\footrulewidth}{0.4pt}

\begin{document}
%---------------------------------------------
%		     TITLE
%---------------------------------------------
\begin{center}
\textbf{\Large Vivitsu Maharaja}
\date{}
\thispagestyle{empty}
\smallskip \\
%---------------------------------------------
%	     CONTACT INFORMATION
%---------------------------------------------
%3800 SW 34\textsuperscript{th} St., Apt. Z251, Gainesville, FL $\vardiamond$ (352) 278-5449 $\vardiamond$ vmaharaja@ufl.edu $\vardiamond$ http://vivitsu.co
http://vivitsu.co
\end{center}

%---------------------------------------------
%	           OBJECTIVE
%---------------------------------------------
%\textbf{OBJECTIVE}
%\smallskip
%\hrule
%To obtain a software developer position where I can leverage and enhance my skills \& experience while working on challenging problems in computer engineering.

%---------------------------------------------
%	           EDUCATION
%---------------------------------------------
\textbf{EDUCATION}
\smallskip
\newline
%\hrule
{\bf Master of Science}, Electrical \& Computer Engineering \hfill May 2014\\
University of Florida, Gainesville, FL. \hfill GPA: 3.33/4.0

{\bf Bachelor of Engineering}, Electronics \& Communication \hfill May 2011\\
Dharmsinh Desai University, Nadiad, India. \hfill GPA: 62/100

%---------------------------------------------
%		WORK EXPERIENCE
%---------------------------------------------
\textbf{EXPERIENCE}
\smallskip
\newline
%\hrule
\textbf{Research Volunteer}, ACIS Lab, University of Florida \hfill May 2013 - May 2014
\begin{itemize}
%---------------------
%	PROJECT - 1
%---------------------
    \item Set up and administered \textbf{Hadoop} \& \textbf{Riak} as \textbf{NoSQL} 
datastores for storing and processing hierarchical data.
    \item Designed a data model for Riak to perform \textbf{clustering} \& \textbf{tokenization} of records. 
    \item Developed middleware in \textbf{Java} to fetch \textbf{JSON} objects 
from a server using \textbf{HTTP} calls \& transform them to POJOs (Plain Old Java Objects).
The middleware also functions as an interface to the Riak cluster.
    \item Evaluated the setup by \textbf{benchmarking} various parameters of the middleware like object fetch time, 
time to commit object to cluster \& JSON parsing time.  
\end{itemize}

\textbf{Embedded Engineer}, Volansys Technologies, Ahmedabad, India \hfill November 2011 - July 2012
\begin{itemize}
%---------------------
%	PROJECT - 1
%---------------------
    \item Developed \& maintained a \textbf{USB 2.0 (EHCI)} driver, to allow 
clients on a LAN to boot using an USB to Ethenet adapter.
    \item Developed components to interface with the \textbf{PCI} \& \textbf{BIOS} 
subsystems in order to manage the complete \textbf{state machine} of the host controller
\& maintain driver compatibility with adapters from multiple vendors. 
%---------------------
%	PROJECT - 2
%---------------------
    \item Developed a network driver in \textbf{C} to allow multiple broadcast 
domains in a router to form a \textbf{VLAN (Virtual LAN)}.
\end{itemize}

%---------------------------------------------
%	          PROJECTS
%---------------------------------------------
\textbf{PROJECTS}
\smallskip 
\newline
%\hrule
%---------------------
%       PROJECT - 1
%---------------------
\textbf{Performance Evaluation of Open vSwitch \& Linux Bridge} \hfill April 2014
\begin{itemize}
    \item Performed a comprehensive evaluation of Linux Bridge \& Open vSwitch software bridges
in multiple configurations.
    \item Designed tests to measure throughput, latency and packet loss between networks of virtual
machines.
\end{itemize}

%---------------------
%	PROJECT - 2
%---------------------
\textbf{Distributed File System} using Java \hfill August 2013 - December 2013
\begin{itemize}
    \item Designed \& implemented a distributed filesystem with a peer-to-peer 
architecture \& chunk based object storage.
    \item Developed software daemons to detect \& react to node failures (fault-tolerance) \& ensure data consistency.  
    \item Developed a multi-threaded client application to communicate with the cluster and store data on the filesystem.
\end{itemize}

%---------------------
%	PROJECT - 3
%---------------------
\textbf{Performance Evaluation of Information Retrieval Systems} using Java \hfill November 2013
\begin{itemize}
    \item Benchmarked the indexing time, compression ratio, recall \& indexing 
algorithm of an Apache Solr retrieval system.
    \item Designed a schema to perform spelling corrections and clustering of 
records using Lucene's Tokenizers \& Analyzers.
    \item Developed an application in Java to automate the record indexing process.
\end{itemize}

%---------------------
%	PROJECT - 4
%---------------------
\textbf{Web Service for Location Based Applications} using Go \& Redis \hfill April 2013
\begin{itemize}
    \item Designed and implemented a multi-threaded HTTP server that serves webpages
based on a user's GPS co-ordinates.
    \item Scaled the server to serve 10,000 HTTP requests per second using goroutines.
    \item Developed a multi-threaded client simulator which makes multiple HTTP requests
to the server using goroutines.
\end{itemize}

%---------------------
%	PROJECT - 5
%---------------------
%{\bf Face Recognition using Artificial Neural Networks} \textit{using C \& CUDA}\hfill{\bf February 2013 - April 2013} \smallskip \\
%Designed and implemented an application that performed face recognition using an artificial neural network on a CPU/GPU cluster. \smallskip
%Used Principal Component Analysis for feature extraction and error backpropagation to train the network. %\medskip

%---------------------
%	PROJECT - 6
%---------------------
\textbf{Distributed Fault-Tolerant Stock Exchange Server} using Java \& JGroups \hfill April 2013
\begin{itemize}
    \item Implemented a stock exchange server that used fault-tolerant, virtually synchronous replicas to perform stock trades.
    \item Enhanced the system so that client information, trade requests \& stock data are preserved across node failures. %\medskip
\end{itemize}

%---------------------
%	PROJECT - 7
%---------------------
%\textbf{Gossip based Topology Management in Peer-to-Peer Systems} \textit{using C} \hfill January 2013
%\begin{itemize}
%    \item Implemented the T-Man gossip based topology management protocol for peer to peer overlay networks, which achieved various topologies for a cluster of nodes based on different distance functions.
%    \item Enhanced the T-Man implementation so that it would adapt it's topology at runtime to changes in the radius of the network. %\medskip
%\end{itemize}

%---------------------
%	PROJECT - 8
%---------------------
%{\bf DNS Server} \textit{using Java RMI}\hfill{\bf February 2013} \smallskip \\
%Implemented a DNS server that supports recursive as well as iterative name resolution with support for server side caching using Java RMI. %\medskip

%---------------------
%	PROJECT - 9
%---------------------
%\textbf{Distributed Control of Currency Exchange Value} \textit{using Java} \hfill March 2013
%\begin{itemize}
%    \item Implemented totally-ordered multicasting using Lamport's logical clocks. 
%    \item Achieved consistent replicas across 3 machines, which shared a currency exchange value, using active replication protocol. %\medskip
%\end{itemize}

%---------------------
%	PROJECT - 10
%---------------------
%{\bf Simulation of Dijkstra's Algorithm} \hfill November 2010
%\begin{itemize}
%    \item Developed a program using C that would take a user-defined network graph as input and find the shortest path between any two nodes in the graph using %Dijkstra's algorithm. %\medskip
%\end{itemize}

%-----------------------------
%	PRESENTATION - 1
%-----------------------------
%{\bf ``Fundamentals of Switching \& Mobile Number Portability in a GSM network''}\hfill{\bf April 2011} \smallskip \\
%Prepared and presented a report on the operation of a large scale GSM network, including switching principles and mobile number portability %implementation. %\medskip

%--------------------------
%   ADDITIONAL PROJECTS
%--------------------------
%\textbf{ADDITIONAL PROJECTS}
%\smallskip
%\newline
Additional projects include 
\textbf{Gossip based Topology Management in Peer-to-Peer Systems} using C,  
\textbf{DNS Server using} Java RMI, 
\textbf{Totally-ordered Multicasting using Lamport's logical clocks} using Java.

%---------------------------------------------
%	           SKILLS
%---------------------------------------------
\textbf{SKILLS}
\smallskip 
%\hrule
\begin{itemize}
    \item C (Proficient), Java (Proficient), Go (Prior experience). Beginner in MPI, CUDA, HTML \& CSS.
    \item Experience with Hadoop, Redis, Riak, Solr, GNU Make, Apache Maven, Git \& SVN.
    \item Knowledge of Data Structures \& Algorithms, Embedded Systems, Virtual Networks.
\end{itemize} 
%Operating Systems: GNU/Linux, OS X, Windows

%------------------
%    COURSEWORK
%------------------
\textbf{COURSEWORK}
\smallskip 
\newline
Computer Architecture, Probability \& Random Processes, Computer Networks, 
Distributed Computing, Cloud Computing, Autonomic Computing, Information Retrieval (Guided Research), Virtual Computers.
\end{document}
